---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# multiforest

This package is a modification (with a very limited scope) of the very nice package `forestmodel` that is available here: [Github](https://github.com/NikNakk/forestmodel)

multiforest will take a dataset and run uni- and multivariate poisson regressions on a binary outcome variable. These plots can take time to construct manually and one nice thing of using this package is that it makes it easy to do compare across sensitivity analyses (like how does results change when this group is excluded, or definition of outcome variable is changed)

## Installation

```{r, eval = FALSE}
devtools::install_github("LarsHernandez/multiforest")
```

# Data

```{r message=FALSE, warning=FALSE}
library(forestmodel)
library(tidyverse)
library(rlang)
library(labelled)
library(survival)
library(pec)

library(multiforest)

source("R/forestmodels_new_test.r")
```

First we need some data, i take some random clinical trial data from the package `pec` and define 5 year survival. It's important only to leave the data that will be contained in the models.

```{r fig.height=7, fig.width=10}
data(Pbc3, package = "pec")

pb <- Pbc3 %>%
  transmute(
    dead5yr = if_else(days < (365 * 5) & status == 2, T, F),
    tment   = if_else(tment == 0, "Placebo", "CyA"),    
    sex     = if_else(sex == 1, "Male", "Female"),
    age = case_when(
      between(age, 0, 50) ~ "18 - 50",
      between(age, 50, 60) ~ "50 - 60",
      between(age, 60, 140) ~ "60 - 75"),
    weight = case_when(
      between(weight, 0, 55) ~ "< 55kg",
      between(weight, 55, 65) ~ "55 - 65kg",
      between(weight, 65, 100) ~ "65 - 100kg"),
    stage = case_when(
      stage < 3 ~ "I-II",
      stage == 3 ~ "III",
      stage == 4 ~ "IV",
      is.na(stage) ~ "IV"),
    unit = case_when(
      unit == 1 ~ "Hvidovre",
      unit == 2 ~ "London",
      unit == 3 ~ "Copenhagen",
      unit == 4 ~ "Barcelona",
      unit == 5 ~ "Munich",
      unit == 6 ~ "Lyon"),
    gibleed = if_else(gibleed == 1, "Yes", "No")) %>%
  mutate(unit  = fct_relevel(unit, "London"),
         tment = fct_relevel(tment, "Placebo"))

head(pb)
```

Before plotting we can make headers a bit nicer by applying a label from the package `labelled` to plot we use the function `mforestmodel` where we have to specify limits and the dependent variable.

```{r fig.height=7, fig.width=10}
var_label(pb) <- list(tment = "Treatment",
                      sex = "Sex",
                      age = "Age group",
                      weight = "Weight group",
                      stage = "Cancer stage",
                      unit = "Hospital",
                      gibleed = "Gastrointestinal bleeding")

source("R/forestmodels_new_test.r")

mforestmodel(pb, dependent="dead5yr", lim=c(-2.4,2.4))
```

There are also a few options included for modifying the plot. For more options just use the raw function code from gíthub. The final plot is a ggplot object, and therefore normal options of ggplot can be supplied, like the labs argument.

```{r fig.height=8, fig.width=10}
mforestmodel(pb, dependent="dead5yr", lim=c(-2.4,2.4), 
             pala="#1f78b4", palb="#a6cee3", 
             legend_position = c(0.55,0.93), 
             spaces = c(0.015,0.22,0.2,0.005,0.2,0.02),
             header = c("Group","Patients","RR of death","Univariate (light)","P","Multivariate (dark)","P")) + 
  labs(title="Relative risk of death within 3 years of diagnosis",
       subtitle="PBC3 - randomized clinical trial between 1 Jan. 1983 and 1 Jan. 1987 ",
       caption="Source: PCB3 from R package pec")
```



Here is another example with some other data

```{r fig.height=6.5, fig.width=10}
data(cgd, package = "survival")

cg <- cgd %>% 
  select(treat, sex, age, hos.cat, status, weight, inherit, height) %>%
  mutate(
    hos.cat = as.character(hos.cat),
    weight = case_when(
      between(weight, 0, 55) ~ "< 55kg",
      between(weight, 55, 65) ~ "55 - 65kg",
      between(weight, 65, 100) ~ "65 - 100kg"),
    height = case_when(
      between(height, 0, 120) ~ "< 1.2m",
      between(height, 120, 150) ~ "1.2 - 1.5m",
      between(height, 150, 220) ~ "1.5 - 2.2m"),
    age = case_when(
      between(age, 0, 10) ~ "0 - 10",
      between(age, 11, 20) ~ "11 - 20",
      between(age, 21, 140) ~ "21 - 40"))
  
var_label(cg) <- list(treat = "Treatment",
                      sex = "Sex",
                      age = "Age group",
                      weight = "Weight group",
                      height = "Height group",
                      hos.cat = "Hospital region",
                      inherit = "Inherited")

mforestmodel(cg, dependent="status", lim=c(-2,2))
```

